|

### 2020-01-12 nontex/install/git/fs_git_setup.Rmd
git setup single repo pull and push

---
title: |
  | Git and Github Example and Tutorial
  | Sync with Multiple Repositories, Store Password etc.
output:
  html_document:
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  pdf_document:
    df_print: paged
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

@@

>>>>

---
title: |
  | Git and Github Example and Tutorial
  | Sync with Multiple Repositories, Store Password etc.
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

@@

## Quick Pull and Push Single Repo and Delete

Suppose temporarily need to work on a repo, but don't want it to take up too much space. Create two bash files with these single repo info

1. initialize
2. secure and pull
3. push 
4. delete

Steps 1 and 2, note do not leave space when defining bash variables around the equality symbol:

```{bash}
#!/usr/bin/bash
STRREPO='EconStatClass'
echo pull single repository
echo going to pull from $STRREPO

# generate all needed key repositories
cd ~
mkdir $STRREPO

# Set global config settings, in ~/.gitconfig
git config --global user.name "Fan Wang"
git config --global user.email wangfanbsg75@live.com

# Initialize
cd ~
cd $STRREPO
git init
git remote add github git@github.com:fanwangecon/$STRREPO

# Secure
eval "$(ssh-agent)"
ssh-add ~/.ssh/id_rsa

# Pull
cd ~
cd $STRREPO
git pull github master

# Open Repository in Atom
atom ~/$STRREPO
```

Steps 3 and 4:

```{bash}
# push
cd ~
cd $STR_REPO
git push -u github master

# remove fully
cd ~
cd $STR_REPO
git rm -r $STR_REPO
```

bash scripts

```{bash}
# change permission to make file an executable
chmod u+x ~/PyFan/bin/pull_one
chmod u+x ~/PyFan/bin/push_one
# execute script
bash ~/PyFan/bin/pull_one
```
